Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-17 manuscript.Rmd
mention figure 3.1 closes #279
fix typo

For `Git` to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
One way to do this is through the visual user interface in the RStudio `Git` pane.
Click on the empty box next to the file you want to stage.
A checkmark then indicates that the file is staged.
After you have staged all of the files you want, click on the commit button, explain in the commit message why you made those changes, and then click on commit.
This stores a snapshot of the current state of the project.

@@

```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN1)
```

>>>>

For `Git` to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
One way to do this is through the visual user interface in the RStudio `Git` pane (see Figure \@ref(fig:modified)).
Click on the empty box next to the file you want to stage.
A checkmark then indicates that the file is staged.
After you have staged all of the files you want, click on the commit button, explain in the commit message why you made those changes, and then click on commit.
This stores a snapshot of the current state of the project.

@@

```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN2)
```
